---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kapow


KAPOW! `r emo::ji("boom")``r emo::ji("explode")``r emo::ji("explode")` Detonate your lists, vectors, and data frames, and then flood your environment with the remains.

### Installation


```{r, eval=FALSE}
devtools::install_github("daranzolin/kapow")
```

### KAPOW! a data frame

```{r}
library(kapow)
kapow(iris)
ls()
```

### KAPOW! after a pipe chain

```{r, message=FALSE, warning=FALSE}
library(dplyr)
crimeEnv <- new.env()
USArrests %>% 
  filter(Murder > 10) %>% 
  mutate(Large_Urban_Pop = if_else(UrbanPop > 75, TRUE, FALSE)) %>% 
  kapow(Murder, Assault, Large_Urban_Pop, envir = crimeEnv)

ls(crimeEnv)
  
```

### KAPOW! a list

```{r}
carsEnv <- new.env()
cars_list <- as.list(mtcars)
kapow(cars_list, list_vars = c("cyl", "mpg", "hp"), obj_prefix_name = TRUE, envir = carsEnv)

ls(carsEnv)
```

### KAPOW! Safety

While explosive, `kapow` is also attentive to your environment and will not overwrite pre-existing values, unless otherwise instructed.

```{r error=TRUE}
kapow(airquality)
kapow(airquality)
kapow(airquality, stop_on_overwrite = FALSE)
```

